The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-04 paper/ms.tex
aigrain and g-m comments

Our dataset includes a rich variety of classical pulsators. We visually inspected the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes. We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, 3~Cepheids, as well as 3~O\,stars 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}. In addition to this, eight stars rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation. The classes we have determined for each star are listed in Table~\ref{table_all}. A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper.

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118). The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901. We gratefully acknowledge financial support by the National Aeronautics and Space Administration through K2 Guest Observer Programs NNX17AF76G, 80NSSC18K0362, and 80NSSC19K0108, which has been essential in bringing this project to fruition.

>>>>

Our dataset includes a rich variety of classical pulsators. We visually inspected the light curves and amplitude spectra to classify all non red-giant stars into traditional variability classes. We identify 23 stars showing $\delta$ Scuti pulsations and 20 with $\gamma$ Doradus pulsations, including 9~with hybrid $\delta$\,Sct/$\gamma$\,Dor variability; 14~slowly pulsating B~stars (SPB stars), 3~$\beta$ Cephei pulsators, and 3~Cepheids; as well as 3~O\,stars and 5~supergiants showing variability \citep[as in][]{Aerts2018,bowman19}. In addition to this, eight stars show rotational modulation, of which two have the characteristics of $\alpha^2$\,CVn chemical spot modulation. The classes we have determined for each star are listed in Table~\ref{table_all}. A detailed frequency analysis of the variability in each star will be presented in a forthcoming paper.

@@

This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute. BJSP also acknowledges the financial support of the Clarendon Fund and Balliol College. TRW acknowledges the support of the Australian Research Council (grant DP150100250) and the Villum Foundation (research grant 10118). SA acknowledges support from the UK Science and Technology Facilities Council (STFC) under grants ST/N000919/1, ST/S000488/1, and ST/R004846/1.

The halo apertures were kindly provided by the K2 team as part of the Guest Observer programs GO6081-7081, GO8025, GO9923, GO10025, GO11047-13047, GO14003-16003, and GO17051-19051, and as a Director's Discretionary Time program in Campaign 4 as GO4901. We gratefully acknowledge financial support by the National Aeronautics and Space Administration through K2 Guest Observer Programs NNX17AF76G, 80NSSC18K0362, and 80NSSC19K0108, which has been essential in bringing this project to fruition.
